### 2013-09-18 chi2014/method.tex
Added a very brief section on data analysis

>>>>

\subsection{Data Analysis}
Throughout this paper, we will fit models to data and give confidence metrics for the parameters of those models. Our analysis techniques are based on Kruschke's \emph{Doing Bayesian Data Analysis: A Tutorial in R and Bugs} \cite{kruschke_doing_2010}. We express our confidence in parameters in terms of the 95\% HDI (highest density interval), or the interval which contains 95\% of the mass of our posterior belief distribution.

To fit the models, we use the Bayesian inference software Stan \cite{stan-software:2013} via the package RStan.
